Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-23 article.tex
wording

\textcolor{red}{DE: la phrase ne veut rien dire}
Considering the short delay of communication between neurons and the slow
decay of fluorescence, the second step of our pipeline consists in identifying
neuron spikes -- characterized by high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}

>>>>

Low frequencies of the signal correspond to the the slow
decay of fluorescence, while communication between neurons are
characterized by short delay. The second step of our pipeline consists in
identifying neuron spikes -- of high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}
